---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/CRC1266-A2/moin.svg?branch=master)](https://travis-ci.org/CRC1266-A2/moin)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# moin

The goal of this package is to allow simple interaction analysis using ideas from gravity models as well as entropy maximizing models in a singly- and a doubly-constrained framework. 

### Citation

Please cite this compendium as:

> Knitter, Daniel (`r format(Sys.Date(), "%Y")`). _MoIn -- Modeling Spatial Interactions_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Installation

You can install MoIn from github with:

```{r gh-installation, eval = FALSE}
if(!require('devtools')) install.packages('devtools')
devtools::install_github("CRC1266-A2/moin")
```

### Licenses

- Text and figures:  
[CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)  
If figures are created by other people these figures are linked to their source location.

- Code:  
See the [DESCRIPTION](DESCRIPTION) file

- Data:   
[CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
