---
title: "Modeling Interactions during the Middle Ages in the Oldenburger Graben"
author: "Daniel Knitter, Alexander Millin"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette 
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

Date source: Wagrien (1649) out of: Domeier K. and M. Haack (1963): Schleswig-Holstein 1652 - Die Landkarten von Johannes Mejer, Husum, aus der neuen Landesbeschreibung der zwei Herzogtümer Schleswig und Holstein von Caspar Danckmerth D. 1652, Verlag Otto Heinevetter, Hamburg-Bergedorf.

**ToDo** What is this example about? 

# Load data

```{r load}
library(sf)
sites <- st_read("data/OldenburgerGraben/Placenames.shp")
roads <- st_read("data/OldenburgerGraben/Routes.shp")

sites$roadconns <- sapply(st_intersects(st_buffer(sites, dist = 10), roads), length)

mapview::mapview(sites, cex = sites$roadconns+1)
```

# Create a network of the sites

## Create Delaunay Graph and calculate the distances between the connected points

```{r eex_del}
library(spdep)
sitesdel <- tri2nb(coords = st_coordinates(sites))
plot(sitesdel, coords = st_coordinates(sites))

distmat <- st_distance(x = sites, y = sites)
distmat <- distmat / 1000

for (i in 1:dim(distmat)[1]) {
  distmat[i,-c(sitesdel[[i]])] <- NA
  }
```

## Network measures as attributes for Interaction

```{r eex_netw, out.width = "100%", out.height = "700px", fig.align = "center"}
g <- igraph::graph_from_adj_list(adjlist = sitesdel,
                                 mode = "all")
sites$degree <- igraph::degree(g)
sites$closeness <- igraph::closeness(g)
sites$betweeness <- igraph::betweenness(g)

knitr::kable(sites)

library(moin)
int_mod <- sc(Oi = sites$rank+1,
              Wj = sites$degree,
              alpha = sites$roadconns+1,
              cij = distmat,
              beta = 1,
              detfun = "power"
              )
sites$Dj <- int_mod$Dj

mapview::mapview(roads) + 
  mapview::mapview(sites,
                   cex = sites$Dj,
                   zcol = "rank")
```

## Todo:

correlate the amount of roads at a site with its Dj value that results from the model with Oi as site rank and Wj as degree centrality
